\documentclass[
	11pt
]{../resume}

\name{Ankur Desai}
\address{(248) $\hspace{-0.1em}$ 657 $\hspace{-0.4em}$ -- $\hspace{-0.4em}$ 3805 \\ ardusa05@gmail.com \\ \href{https://ardusa.github.io/}{ardusa.github.io} \\ \href{https://linkedin.com/in/ardusa/}{linkedin.com/in/ardusa}}

\begin{document}
	\begin{rSection}{E}{ducation}
		\begin{rSectionEntry}{Michigan State University}{Expected, May 2028}{B.S. in Computer Science}{}{East Lansing, MI}
			\item GPA: 3.74 / 4.0
			% \item Involvement: VP of Claude Builder Club, Eagle Scout
			\item Relevant Coursework: Linear Algebra, Discrete Mathematics, Object-Oriented Software Design, Computer Organization and Architecture, Data Structures \& Algorithms
		\end{rSectionEntry}
	\end{rSection}

	\begin{rSection}{E}{xperience}
		\begin{rSectionEntry}{Michigan State Unmanned Systems Team}{November 2025 -- Present}{Software Engineer --- Autonomous Systems}{}{East Lansing, MI}
			\item Developed autonomous drone software on Nvidia Jetson using MAVLink and Orange+ Flight controller.
			\item Engineered autonomous payload delivery system capable of releasing packages from 70+ feet altitude with a precision of $\pm7$ feet.
			\item Built a machine learning pipeline: curated a 5,000+ aerial image dataset and optimized YOLOv11 inference using TensorRT on embedded CUDA hardware, achieving 79\% detection accuracy at 30 FPS.
			\item Researched and implemented advanced path-planning; compared A* and Dijkstra's algorithms, developing a custom A* based solution for efficient multi-waypoint autonomous navigation.
		\end{rSectionEntry}

		\begin{rSectionEntry}{ThinkStack --- Relationship Powered Note Taking Tool}{September 2025 -- November 2025}{Project Lead}{React, Tailwind CSS, FastAPI, Neo4j, PostgreSQL}{East Lansing, MI}
			\item Led agile SCRUM team of 6 software engineers, coordinating sprints and communicating goals with client.
			\item Streamlined collaboration with CI/CD pipelines, boosting unit test code coverage to 87\%.
			\item Built a modular React web app with Vite and Tailwind CSS for rapid and responsive styling, component-based architecture, efficient batching algorithms using the marked library, and OAuth2.0 authentication.
			\item Designed and implemented containerized RESTful API with secure JWT-based authentication and CORS middleware, integrating PostgreSQL and Neo4j in a cohesive dual-database architecture.
		\end{rSectionEntry}
	\end{rSection}

	\begin{rSection}{P}{rojects}
		% \begin{rSectionEntry}{box.io --- Immersive Browser-Based 3D Boxing Application}{December 2025 -- Present}{System Design}{React, Node.js, Express.js, MongoDB, Three.js, MediaPipe, Tailwind}{}
		% 	\item Developing a browser-based 3D boxing application using React and Three.js, integrating real-time animations and 3D object interactions with React Three Fiber.
		% 	\item Leveraging Vite and Tailwind CSS for fast development and optimized builds, while enforcing TypeScript-based type safety and code quality through robust linting workflows.
		% \end{rSectionEntry}

		\begin{rSectionEntry}{Mira --- AI Personal Assistant}{May 2025 -- Present}{Full-Stack Development}{Python, FastAPI, NLP, PostgreSQL, OAuth, WebSocket, Next.js}{}
			\item Deployed a containerized FastAPI backend on AWS Lambda and AWS RDS, integrating Gemini API and optimizing with asynchronous processing, lazy loading, and dependency injection.
			\item Developed Retrieval-Augmented Generation (RAG) pipelines, utilized sentiment analysis and Named Entity Recognition to disambiguate user commands by augmenting context with relevant prior information.
			\item Increased Whisper model accuracy by 63\% through spectral gating, denoising, and dynamic gain control.
			\item Built a cross-platform Electron and Next.js desktop client for real-time voice command processing, integrating RTC-based Voice Activity Detection (VAD) for low-latency audio processing.
			\item Implemented OAuth2 authentication with CORS middleware, integrated OS keychain for secure credential storage, empowering cloud-based infrastructure for real-time synchronization and WebSocket updates.
			% \item Architected distributed multi-device system with intelligent client selection algorithm using proximity scoring and ambient noise analysis, enabling seamless voice command routing across multiple endpoints.
		  	% \item Integrated OpenAI Whisper, spaCy and the Google Gemini API for voice transcription, natural language processing, and sentiment analysis, processing 1,000+ daily interactions through robust error handling and lazy-loading.
		  	% \item Deployed microservices architecture on AWS Lambda, implementing JWT authentication, Redis caching, and PostgreSQL query optimization.
		\end{rSectionEntry}

		\begin{rSectionEntry}{WizViz --- Multiplayer AR Wizard Game}{February 2025}{SpartaHack X}{Python, OpenCV, MediaPipe, PyGame}{\href{https://devpost.com/software/wizviz}{Devpost Link}}
			\item Developed real-time multiplayer AR wizard-duel game using OpenCV and PyGame, winning the Interactive Media track among 100+ projects and 350+ participants at SpartaHack X.
			\item Built a custom physics game engine with collision detection for gesture-based controls and interactions.
			\item Used MediaPipe Pose for skeletal tracking of 2 players on 33 landmarks with sub-30ms at 60 FPS.
		\end{rSectionEntry}
	\end{rSection}

	\begin{rSection}{T}{echnical Skills}
		\begin{rSet}{Languages}{Python, Java, C/C++, JavaScript/TypeScript, HTML5, CSS3, SQL, Bash}
		\end{rSet}
		\begin{rSet}{Frameworks}{React, Vite, Node.js, Electron, FastAPI, SQLAlchemy, REST APIs, Tailwind}
		\end{rSet}
		\begin{rSet}{Databases}{PostgreSQL, Neo4j, AWS RDS, Redis}
		\end{rSet}
		\begin{rSet}{Cloud \& DevOps}{Docker, Git, CI/CD, AWS (Lambda, EC2, ECS), Google Cloud}
		\end{rSet}
		% \begin{rSet}{Core Competencies}{Full-Stack Development, RESTful API Design, Object-Oriented Programming,
		% 	Database Design, Test-Driven Development, System Architecture, Agile/SCRUM, Code Review, Problem Solving}
		% \end{rSet}
	\end{rSection}

\end{document}