\documentclass[
	11pt
]{resume}

% \usepackage{ebgaramond} % Use the EB Garamond font
\usepackage{fontspec}
\usepackage{hyperref}
\setmainfont{Times New Roman}

%------------------------------------------------

\name{Ankur Desai}

\address{49032 Freestone Dr. \\ Northville, MI 48168}
\address{591 N. Shaw Ln. \\ East Shaw Hall Room 131 \\ East Lansing, MI 48825}
\address{(248) $\cdot$ 657 $\cdot$ 3805 \\ ardusa05@gmail.com \\ \href{https://ardusa.github.io/}{ardusa.github.io}}

\begin{document}
	\begin{rSection}{Education}
		\begin{rSectionEntry}{Michigan State University}{May 2028}{B.S. in Computer Science \& Engineering}{East Lansing, MI}
			\item GPA: 3.735
			\item Relevant Coursework: Linear Algebra, Discrete Mathematics, Calculus 3
		\end{rSectionEntry}
	\end{rSection}

	\begin{rSection}{Experience}
		\begin{rSectionEntry}{WFS Consulting Group}{May 2025 -- Present}{Web Developer}{Plymouth, MI}
			\item Designed and deployed a responsive company website, improving client visibility and online engagement.
			\item Met with consulting clients to translate business requirements into technical solutions.
			\item Implemented cross-device compatibility for a smooth user experience.
		\end{rSectionEntry}

		\begin{rSectionEntry}{Target}{June 2024 -- Aug 2024}{Customer Service Advocate}{Northville, MI}
			\item Assisted 50+ customers daily with complex inquiries, reinforcing a core principle of Customer Obsession.
			\item Collaborated with team members to resolve escalated issues, reducing customer wait times during peak hours.
			\item Developed communication and conflict resolution skills under fast-paced conditions.
		\end{rSectionEntry}
	\end{rSection}

	\begin{rSection}{Projects}
		\begin{rSectionEntry}{Mira Personal Assistant}{May 2025 -- Present}{Full-Stack Development}{}
			\item Built a cross-platform desktop application using Node.js and Electron for task automation.
			\item Developed a RESTful API with FastAPI + SQLAlchemy, enabling storage and retrieval of structured tasks, conversation history, and user profiles.
			\item Integrated Hugging Face Transformers for NLP, allowing the assistant to classify and respond to user input, and respond to wake words.
			\item Implemented embeddings + DBScan clustering for user voice tracking intent recognition, and sentiment recognition.
			\item Utilized LM Studio to train multiple custom language models for improved task understanding and completion.
		\end{rSectionEntry}

		\begin{rSectionEntry}{WizViz (SpartaHack X)}{February 2025}{Hackathon Project}{\href{https://devpost.com/software/wizviz}{Devpost Link}}
			\item Collaborated with 3 peers to design a computer vision based game using PyGame + OpenCV.
			\item Won Best Game Award among 300+ participants for creativity and technical execution.
		\end{rSectionEntry}

		\begin{rSectionEntry}{Personal Portfolio Website}{February 2025 -- Present}{Web Development}{\href{https://ardusa.github.io/}{ardusa.github.io}}
			\item Created a personal portfolio website with HTML, CSS, and JavaScript to showcase projects.
			\item Continuously expand features (e.g., blog, project demos), with 200+ unique monthly visitors.
		\end{rSectionEntry}
	\end{rSection}

	\begin{rSection}{Leadership \& Activities}
		\begin{rSectionEntry}{Eagle Scout - Boy Scouts of America}{December 2019}{Leadership}{}
			\item Planned and executed a community service project with 200+ volunteer hours.
			\item Coordinated logistics, fundraising, and led a 10-person team to successful completion, accumulating 120+ volunteer hours.
		\end{rSectionEntry}

		\begin{rSectionEntry}{Northville Robostangs}{2022 - 2024}{Software \& Electrical/Pneumatics Captain}{Northville, MI}
			\item Led a team of 15 students in programming FRC competition robots.
			\item Implemented vision-based autonomous routines, improving competition performance.
			\item Coordinated cross-functional integration of software and hardware systems for reliability during matches.
			\item Mentored junior members in coding best practices and robotics concepts.
		\end{rSectionEntry}

		\begin{rSectionEntry}{Imagine Software Club}{2024 - Present}{Member}{East Lansing, MI}
			\item Engaging in software development projects and hackathons.
			\item Collaborating with peers to create innovative solutions and applications.
		\end{rSectionEntry}

		\begin{rSectionEntry}{Unmanned Systems}{2025 - Present}{Member}{East Lansing, MI}
			\item Collaborating on projects involving drone technology and autonomous systems.
			\item Competed in the SUAS (Student Unmanned Aerial Systems) competition, showcasing drone capabilities.
		\end{rSectionEntry}
	\end{rSection}

	\begin{rSection}{Technical Skills}
		\begin{rSet}{Languages}{Java, Python, JavaScript, HTML/CSS}
		\end{rSet}
		\begin{rSet}{Frameworks \& Tools}{React, Node.js, FastAPI, SQLAlchemy}
		\end{rSet}
		\begin{rSet}{Databases}{MySQL}
		\end{rSet}
		\begin{rSet}{Other}{REST APIs, JSON, Git/GitHub}
		\end{rSet}
	\end{rSection}

\end{document}
