\documentclass[
	11pt
]{../resume}

\usepackage{fontspec}
\usepackage{hyperref}
\setmainfont{Times New Roman}

\name{Ankur Desai}
\address{(248) $\hspace{0.01em}$ 657 - 3805 \\ ardusa05@gmail.com \\ \href{https://ardusa.github.io/}{ardusa.github.io} \\ \href{https://linkedin.com/in/ardusa/}{linkedin.com/in/ardusa}}

\begin{document}
	\begin{rSection}{E}{ducation}
		\begin{rSectionEntry}{Michigan State University}{Expected, May 2028}{B.S. in Computer Science}{East Lansing, MI}
			\item GPA: 3.74 / 4.0
			\item Vice President of Claude Builders Club @ MSU
			\item Relevant Coursework: Linear Algebra, Discrete Mathematics, Object-Oriented Software Design, Computer Organization and Architecture, Data Structures \& Algorithms
		\end{rSectionEntry}
	\end{rSection}

	\begin{rSection}{E}{xperience}
		\begin{rSectionEntry}{Machine Learning Team}{September 2025 - Present}{Unmanned Systems}{East Lansing, MI}
			\item Architected autonomous drone software on Nvidia Jetson implementing real-time sensor fusion (GPS, IMU, barometer), integrating YOLOv11 object detection for autonomous navigation with obstacle avoidance at 24 FPS.
			\item Engineered end-to-end machine learning pipeline: curated 5,000+ aerial image dataset, applied data augmentation techniques, and optimized YOLOv11 inference using TensorRT on embedded hardware.
			\item Integrated computer vision system with Cube Orange+ flight controller via MAVLink protocol, enabling vision-based position hold and autonomous payload delivery within 10-foot precision from 70+ feet altitude.
		\end{rSectionEntry}

		\begin{rSectionEntry}{Web Development Intern}{May 2025 - August 2025}{WFS Consulting Group}{Plymouth, MI}
			\item Designed and developed a responsive website using HTML5, CSS3, and JavaScript, ensuring consistent performance across Chrome, Firefox, Safari, and Edge.
			\item Reached 95+ Google Lighthouse scores boosting engagement by 250\% through contact forms and Google Analytics.
			\item Deployed production website to Linux servers with Apache and SSL certificates, maintaining 99.9\% uptime.
		\end{rSectionEntry}
	\end{rSection}

	\begin{rSection}{P}{rojects}
		\begin{rSectionEntry}{ThinkStack}{August 2025 - Present}{Project Team Lead | React, Tailwind, FastAPI, Neo4j, PostgreSQL}{East Lansing, MI}
			\item Architected a full-stack React web application with component-based design, enabling real-time CRUD operations and integrating authentication and role-based access using FastAPI, SQLAlchemy ORM, and PostgreSQL.
			\item Engineered seamless integration with Neo4j to support dynamic relationship queries for advanced data models.
			\item Led a team of 6 through Agile/SCRUM, automating CI/CD pipelines with Jest and Pytest, with 87\% code coverage.
		\end{rSectionEntry}

		\begin{rSectionEntry}{Mira - AI Personal Assistant}{May 2025 - September 2025}{Full-Stack Development | Python, FastAPI, SQL, Electron, React}{\href{https://github.com/mira-assistant}{GitHub Link}}
			\item Engineered audio processing pipeline with noise reduction using spectral gating, improving OpenAI Whisper speech recognition from 78\% to 95\% accuracy in noisy environments (SNR < 10dB).
			\item Developed natural language processing pipeline integrating Whisper for transcription, DBSCAN for speaker diarization, and Sentence Transformers for intent classification, processing 1,000+ daily interactions with 92\% accuracy.
			\item Implemented intelligent client selection algorithm using RSSI proximity estimation and FFT ambient noise analysis for dynamic command routing with 89\% selection accuracy.
		\end{rSectionEntry}

		\begin{rSectionEntry}{WizViz - SpartaHack X}{February 2025}{Hackathon | Python, OpenCV, MediaPipe, PyGame}{\href{https://devpost.com/software/wizviz}{Devpost Link}}
			\item Built a real-time multiplayer AR game using OpenCV and PyGame, achieving 60 FPS on Windows and MacOS.
			\item Implemented gesture-based controls and custom physics engine with collision detection for 2-player wizard duels.
			\item Used MediaPipe Pose for skeletal tracking on 33 landmarks with sub-30ms latency; won Interactive Media track among 100+ projects and 350+ participants at SpartaHack X.
		\end{rSectionEntry}
	\end{rSection}

	\begin{rSection}{T}{echnical Skills}
		\begin{rSet}{Languages}{Python, Java, C/C++, JavaScript/TypeScript, HTML5, CSS3, SQL, Bash}
		\end{rSet}
		\begin{rSet}{Libraries}{TensorFlow, PyTorch, OpenCV, MediaPipe, YOLOv11, NumPy, Sentence Transformers}
		\end{rSet}
		\begin{rSet}{Databases}{PostgreSQL, Neo4j, AWS RDS}
		\end{rSet}
		\begin{rSet}{Frameworks}{React, Vite, Node.js, Electron, FastAPI, SQLAlchemy, Tailwind CSS}
		\end{rSet}
		\begin{rSet}{Cloud \& DevOps}{Docker, Git, CI/CD Pipelines, AWS (Lambda, EC2, Cloudwatch), Google Cloud Platform}
		\end{rSet}
	\end{rSection}

\end{document}